Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Article overview

>>>>

\subsection*{Overview of the article}

We have sofar frame our intents: to design a robotic system that would support
handwriting remediation in an original way: by getting children to teach a
robotic agent how to write, those children would both practise without knowing
it and recover self-confidence and self-esteem by supporting a
worst-than-themselves robotic ``student''.

The following sections of the paper go into details. The next section provides a
brief overview of the robotic system and the interaction it induces. We then
give the details of machine-learning techniques that allow the robot to learn
from the children, followed by the implementation on the Nao robot.

Next, we present and report on the four school experiments and the two case
studies that we conducted over the last two years. While the focus of the school
experiments was mostly technical validation and data acquisition, the two case
studies that lasted each about 4 weeks, gave us initial insights on the
relevance and effectiveness of our approach.
